### 2014-11-11 contract-language.tex
Typo
Added untyped effvar quantification to contracts

\begin{figure}
\vspace{-7pt}
\begin{smathpar}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

The syntax of our core contract language is shown in Figure
~\ref{fig:contract-lang}. The language is based on first-order logic (FOL), and
admits prenex universal quantification over typed effect variables. We use a
special effect variable ($\cureff$) to denote the effect of \emph{current
operation} - the operation for which a contract is being written. The type of
an effect is simply the name of the operation (eg: \cf{withdraw}) that induced
the effect. We admit disjunction in types to let an effect variable range over
multiple operation names. The contract $\small \forall (a : \tau_1 \vee
\tau_2).~\psi$ is just syntactic sugar for $\small \forall a. (\oper{a}{\tau_1}
\vee \oper{a}{\tau_2}) \Rightarrow \psi$.

@@

We now present a meta-theoretic result that certifies the soundness of
classification-based contract enforcement. To help us state the result, we
define an operational semantics of the our system described informally in
\S~\ref{sec:sysmod}:

>>>>

\begin{figure}
\vspace{-7pt}
\begin{smathpar}
\begin{array}{rclcl}
\multicolumn{5}{c}{
  {x,y,\cureff} \in \mathtt{EffVar} \qquad \qquad
  {\sf Op} \in \mathtt{OperName}
}\\
\cv 		& \in & \mathtt{Contract} 	& \coloneqq & \forall (x : \tau).\cv
        \ALT \forall x.\cv \ALT \pi \\
\tau		& \in	& \mathtt{EffType}	& \coloneqq &  {\sf Op}
        \ALT \tau \vee \tau \\
\pi			&	\in & \mathtt{Prop} & \coloneqq & \true \ALT R(x,y)
        \ALT \pi \vee \pi \\
			  & 		&	 &  \ALT & \pi \wedge \pi \ALT \pi \Rightarrow \pi \\
R				& \in & \mathtt{Relation}	& \coloneqq & \visZ \ALT \soZ
        \ALT \sameobjZ \ALT R^+ \\
				&			&	 &  \ALT & R \cup R \ALT R \cap R \\
\end{array}
\end{smathpar}
\caption{Contract language.}
\label{fig:contract-lang}
\end{figure}

@@

The syntax of our core contract language is shown in Figure
~\ref{fig:contract-lang}. The language is based on first-order logic (FOL), and
admits prenex universal quantification over typed and untyped effect variables.
We use a special effect variable ($\cureff$) to denote the effect of
\emph{current operation} - the operation for which a contract is being written.
The type of an effect is simply the name of the operation (eg: \cf{withdraw})
that induced the effect. We admit disjunction in types to let an effect variable
range over multiple operation names. The contract $\small \forall (a : \tau_1
\vee \tau_2).~\psi$ is just syntactic sugar for $\small \forall a.
(\oper{a}{\tau_1} \vee \oper{a}{\tau_2}) \Rightarrow \psi$. An untyped effect
variable ranges over all operation names.

@@

We now present a meta-theoretic result that certifies the soundness of
classification-based contract enforcement. To help us state the result, we
define an operational semantics of the system described informally in
\S~\ref{sec:sysmod}:
